Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2016-02-17 documents/ms/ms.tex
comments from Hogg

\remove{We propose and advise dealing with}\revise{We propose to militate} these variations in \Kepler\ light-curves by \emph{modeling} them.
In this context, a model is \remove{(at least)} a parameterized function that can predict data, given parameter settings,
  and an objective function that can be used to set or sample those parameters.
In some cases, the objective function can be given a probabilistic justification or interpretation, e.g., if it is constructed using a likelihood and a prior pdf.
The model can be a physical model (of the spacecraft PSF, pointing, temperature, and so on)
  or it can be a flexible, effective model that has no direct interpretation in terms of physical spacecraft parameters.
If done well, we would expect a physical model to do a better job,
  because it embodies more prior information,
  but it requires research and intuition about dominant effects. 
If this research and intuition is wrong or incomplete, a physical model may actually perform worse.
The model we propose here is in the non-physical, effective category.
The \Kepler\ community is familiar with these kinds of models;
  to our knowledge, \emph{all} successful light-curve ``de-trending'' methods
  are flexible, effective models.

@@

\section{Discussion}
We have presented a simple yet highly effective method---the \name---that works at pixel-level \revise{to remove spacecraft and stellar variability on time-domain imaging. It is} based on the causal structure of the \Kepler\ data \remove{to}\revise{; It} calibrates the \Kepler\ light-curves \remove{, which is intended to search exoplanets.} \revise{for the purpose of exoplanet search.}
In \revise{the} \name, systematics and stellar variabilities are removed by
  either fitting with other stars' light-curves or auto-regressive components, while transit signals \remove{can still be perfectly preserved} \revise{are preserved with a} \remove{by} train-and-test framework.
Low variable clean light-curves can be produced by \name\,  
  which is ideal for transit planet searching. 
The CDPP noise level estimation is also presented in the paper to show the performance of \name.

>>>>

\remove{We propose and advise dealing with}\revise{We propose to mitigate} these variations in \Kepler\ light-curves by \emph{modeling} them.
In this context, a model is \remove{(at least)} a parameterized function that can predict data, given parameter settings,
  and an objective function that can be used to set or sample those parameters.
In some cases, the objective function can be given a probabilistic justification or interpretation, e.g., if it is constructed using a likelihood and a prior pdf.
The model can be a physical model (of the spacecraft PSF, pointing, temperature, and so on)
  or it can be a flexible, effective model that has no direct interpretation in terms of physical spacecraft parameters.
If done well, we would expect a physical model to do a better job,
  because it embodies more prior information,
  but it requires research and intuition about dominant effects. 
If this research and intuition is wrong or incomplete, a physical model may actually perform worse.
The model we propose here is in the non-physical, effective category.
The \Kepler\ community is familiar with these kinds of models;
  to our knowledge, \emph{all} successful light-curve ``de-trending'' methods
  are flexible, effective models.

@@

\section{Discussion}
We have presented a simple yet highly effective method---the \name---that works at pixel-level \revise{to remove spacecraft and stellar variability on time-domain imaging. It is} based on the causal structure of the \Kepler\ data \remove{to}\revise{; It} calibrates the \Kepler\ light-curves \remove{, which is intended to search exoplanets.} \revise{for the purpose of exoplanet search.}
In \revise{the} \name, systematics and stellar variabilities are removed by
  either fitting with other stars' light-curves or auto-regressive components, while transit signals \remove{can still be perfectly preserved} \revise{are preserved with a} \remove{by} train-and-test framework \revise{to control model freedom}.
Low variable clean light-curves can be produced by \name\,  
  which is ideal for transit planet searching. 
The CDPP noise level estimation is also presented in the paper to show the performance of \name.
